An investigation into using scagnostics to find interesting projections of high-dimensional data

### 2018-10-01 scagnostics.Rmd
tweaks
References added, but something is broken, caching needs to be fixed first.

```{r initial, echo = FALSE, cache = TRUE, include = FALSE}
library(knitr)
opts_chunk$set(
  warning = FALSE, message = FALSE, echo = FALSE, 
  fig.path = 'figure/', cache.path = 'cache/', fig.align = 'center', 
  fig.show = 'hold', cache = FALSE, external = TRUE, dev = "pdf",
  fig.height = 5, fig.width = 8, out.width = "\\textwidth"
)
```

@@

- Some metrics for exploring high-dimensional data by finding interesting pairs of variables, can be used to find interesting projections, but some have problems. 
- What are the ways to evaluate.
- What adjustments can be done.
- How it can be applied
-->

@@

- Motivation first?
- PP
- Scagnostics
- section needs shortening

@@

[REF] (Katrin's thesis) explored the behaviour of scagnostics for selecting variables, and proposed two more, based on smoothing splines that have some nicer properties. In addition the availability of another two indices based on information criteria, maximal and total information coefficient (MIC and TIC) [@Reshef1518] round out our collection of metrics. These indices are all available in R packages, scagnostics [@HWscagR], mbgraphic [@mbgraphic] and minerva [@minerva]. The projection pursuit guided tour is available in the R package, tourr [@tourr].

@@

<!-- index values shouldn't be affected by sample size, on average it should be
same value. Maybe some need to be normalised by n. Something needs fixing here.
-->

>>>>

```{r initial, echo = FALSE, cache = TRUE, include = FALSE}
library(knitr)
opts_chunk$set(
  warning = FALSE, message = FALSE, echo = FALSE, 
  fig.path = 'figure/', cache.path = 'cache/', fig.align = 'center', 
  fig.show = 'hold', cache = TRUE, external = TRUE, dev = "pdf",
  fig.height = 5, fig.width = 8, out.width = "\\textwidth"
)
```

@@

- Some metrics for exploring high-dimensional data by finding interesting pairs of variables, can be used to find interesting projections, but some have problems. 
- What are the ways to evaluate.
- What adjustments can be done.
- How it can be applied

@@

- Motivation first?
- PP
- Scagnostics
- section needs shortening
-->

@@

[@Grimm2018] explored the behaviour of scagnostics for selecting variables, and proposed two more, based on smoothing splines that have some nicer properties. In addition the availability of another two indices based on information criteria, maximal and total information coefficient (MIC and TIC) [@Reshef1518] round out our collection of metrics.\footnote{It is interesting to note that entropy, closely related to the notion of mutual information, has previously been considered as a projection pursuit index when searching for interesting one-dimensional projections, see @nason1992, @NIPS1997_1408.} These indices are all available in R packages, scagnostics [@HWscagR], mbgraphic [@mbgraphic] and minerva [@minerva]. The projection pursuit guided tour is available in the R package, tourr [@tourr].

@@

<!-- index values shouldn't be affected by sample size, on average it should be
same value. Maybe some need to be normalised by n. Something needs fixing here.

can we get "theoretical" min/max values, to assess the scale of the index for any particular data set.
-->
